A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-16 paper.tex
modify "fine grained dependency manamgement" section

The difficulty of data access authority acquisition enforces us to find out one
solution, in which the reproduction of the original analysis can be done
without any external dependency. That is, one independent and self-contained
package containing all the data and software dependencies is necessary.

Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package. 
One reason is that figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and the original author is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physists.

To generate one self-contained and independent package for one experiment, all
the clear and implicit dependencies must be figured out firstly. The map mechanism
of Solution 3 can provide clear data and software dependencies. As for the
implicit dependencies, directly preserving the whole OS together with the data
stored on the disk of the original machine or the data from other filesystems
mounted as local filesystems, such as HDFS and PanFS, is not feasible. One
efficient mechanism which can figure out the really used parts of all these
filesystems is necessary. The requirements of the underlying OS and hardware
architecture can be easily found with system tools such as uname or
lsb\_release.

Then one new package including all the data and software dependencies can be generated and published. 
One packaging utility is necessary for the original author to generate the package. 
To multiplex the common data which is involved in different experiments, such as OS images and common software libraries, the data of different packages will be rearranged and categorized in the archive.
One description file, which includes the experiment aim, dependency list,  package size and relevant information, will be generated for each package.

@@

Table~\ref{table:archive-map} illustrates the structure of the remote archive.
Item {\tt /archive/OS} includes the images of different Operating Systems.
Item {\tt /archive/software} integrates all the commonly used software, such as git,
python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
Grid. Item {\tt /archive/experiment} includes the all the experiments submitted into the
archive. The private files and description files of each experiment will be
organized together.

The Version 4 of Table~\ref{table:scripts} illustrates the script used in
Solution 4, which is the same as the one used in Solution 3. 
However, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file redirects the git access path into {\tt /archive/git} from the original path (\path{http://github.com}) referred in the script.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the archive only introduces the minimal changes of the map file on the client side.

@@

\section{One Implementation of Fine-Grained Toolkit Using Parrot}

>>>>

The difficulty of data access authority acquisition enforces us to find out one
solution, in which the reproduction of the original analysis can be done
without any external dependency. One independent and self-contained
package containing all the data and software dependencies is necessary. 
Two questions must be answered for this aim.

{\bf First, who should be responsible to generate the package?}
Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package is unrealistic. 
Figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and the original author is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physists.
Therefore, one packaging utility is necessary to help the original author to generate the package.

{\bf Second, how to figure out the implicit dependencies?}
With the help of the formulated script, we can easily figure out the explicit dependencies.
The requirements of the underlying OS and hardware
architecture can be easily found with system tools such as uname or
lsb\_release.
However, how to figure out the implicit dependencies needs more concerns, because
directly preserving the whole OS together with the data
stored on the disk of the original machine or the data from other filesystems
mounted as local filesystems, such as HDFS and PanFS, is not feasible. One
efficient mechanism which can figure out the really used parts of all these
filesystems is necessary. 
To do this, the file access details of the application should be tracked and utilized.

@@

Table~\ref{table:archive-map} illustrates the structure of the remote archive.
To multiplex the common data which is involved in different experiments, such as OS images and common software libraries, the data of different packages will be rearranged and categorized in the archive.
Item {\tt /archive/OS} includes the images of different Operating Systems.
Item {\tt /archive/software} integrates all the commonly used software, such as git,
python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
Grid. Item {\tt /archive/experiment} includes the all the experiments submitted into the
archive, each sub-item should include the private files and description files of each experiment.

One map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file redirects the git access path into {\tt /archive/git} from the original path (\path{http://github.com}) referred in the script.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the archive only introduces the minimal changes of the map file on the client side.

@@

\section{One Fine Grained Dependency Management Toolkit Based on Parrot}
